### 2020-03-23 tex/confirm-service-activity/prelim.tex
reorganize the document

\section{Preliminaries}
\label{prelim}
This section provides an overview of two concepts that we use in the 
proposed solutions. These include the framework of proof carrying data (PCD) 
and the collective signing (CoSi) protocol.

\subsection{Proof Carrying Data (PCD)}
The paradigm of PCD~\cite{chiesa2010proof} allows proving to the correctness of a distributed 
computation involving untrusted parties. It produces a single proof for the output 
that attests not only the correctness of the final result, but also 
the correctness of the entire history of intermediate computations that produced 
this result. Correctness here is defined as a polynomially computable predicate that 
abstracts the properties, or invariants, that must be satisfied.

@@

\subsection{Collective Signing (CoSi)}
\label{cosi}
CoSi~\cite{syta2016keeping} is a protocol that enables a set of distributed parties to cosign a 
statement together in a way that produces a single signature. As such, both the 
verification time and the space requirements are just like having a single signer. The 
difference is that this signature attests that all parties agree with the signed 
statement instead of only one.

>>>>

\subsection{Preliminaries}
\label{prelim}
This section provides an overview of two concepts that we use in the 
proposed solutions. These include the framework of proof carrying data (PCD) 
and the collective signing (CoSi) protocol.

\subsubsection{Proof Carrying Data (PCD)}
The paradigm of PCD~\cite{chiesa2010proof} allows proving to the correctness of a distributed 
computation involving untrusted parties. It produces a single proof for the output 
that attests not only the correctness of the final result, but also 
the correctness of the entire history of intermediate computations that produced 
this result. Correctness here is defined as a polynomially computable predicate that 
abstracts the properties, or invariants, that must be satisfied.

@@

\subsubsection{Collective Signing (CoSi)}
\label{cosi}
CoSi~\cite{syta2016keeping} is a protocol that enables a set of distributed parties to cosign a 
statement together in a way that produces a single signature. As such, both the 
verification time and the space requirements are just like having a single signer. The 
difference is that this signature attests that all parties agree with the signed 
statement instead of only one.

### 2020-03-23 tex/confirm-service-activity/solutions.tex
reorganize the document

\section{Potential Solutions}
\label{solutions}
This section outlines several potential solutions for how to let Ursula prove 
that she served a given number of distinct requests in a publicly verifiable way. 
One of these solutions, the PCD-based one, is still a work in progress. The goal 
is to share the high-level idea of each of these solutions and to chose the best one,
after we define the meaning of best, to be adopted by the NuCypher network.

\subsection{PCD-based Scheme}
The main idea here is to adapt the PCD framework so that Ursula
can combine the correctness proofs she computes for Bobs' requests in a single proof 
attesting to the following fact: ``Ursula has served $\omega$ distinct re-encryption 
requests correctly."

@@

\subsection{CoSi-based Scheme}
This solution utilizes the idea of collective signing by electing a committee 
that will sign a report submitted by a specific Ursula after verifying that 
the report supports the claim that ``Ursula has served $\omega$ distinct 
re-encryption requests correctly."

@@

\subsubsection{On the committee election.} This can be done
by using some deterministic computation over a block hash and mapping
the output to Ursulas' public keys. So the selection is not determined by the
working Ursula to prevent any potential collusion. The selection may also take into account the presence and size of each Ursula's stake, to avoid an attacker spinning up enormous numbers of Ursulas in order to increase the chance of them controlling the entire committee.

@@

\subsubsection{On the publicity of the signed records.} Having a 
valid collective signature from a committee (that has at least one honest 
member) suffices for the correctness of the signed statement. However, 
it could be better to keep the records that produced the message $m$  
available for a while so that any party can verify them (the verifying
parties could maintain such a public record for a given period after which
the logs can be discarded).

@@

\subsubsection{On compensating the committee.} This solution may 
raise the question of why would the elected committee (especially if it 
is composed of other Ursulas in the system) participate in the CoSi 
process, which also involves verifying the full request record presented 
by the working Ursula. This can be pictured as a collaborative
work, the committee does the work so that others will do the same
when the committee members play the role of working Ursulas.

@@

\subsection{Challenge/Open-based Scheme}
This solution utilizes the idea of commit/challenge/open protocols. 
In details, Ursula keeps track of the requests coming from Bob(s) 
during a time round and assign each of them a unique sequence 
number. That is, Ursula replies with $cFrag$ and the correctness proof 
along with a sequence number showing the order of the request within 
the batch of requests handled during a round. At the end of the round, 
Ursula constructs a Merkle tree of all requests, where 
the requests (and their replies) are the leaves of the tree ordered by the sequence
numbers. Ursula signs the root of the tree, denoted as $root$ to produce 
a signature $\sigma_{root}$, then it publishes $(\omega, root, \sigma_{root})$ 
to the network (recall that $\omega$ is the number of served requests).

>>>>

\subsection{Potential Solutions}
\label{solutions}
This section outlines several potential solutions for how to let Ursula prove 
that she served a given number of distinct requests in a publicly verifiable way. 
One of these solutions, the PCD-based one, is still a work in progress. The goal 
is to share the high-level idea of each of these solutions and to chose the best one,
after we define the meaning of best, to be adopted by the NuCypher network.

\subsubsection{PCD-based Scheme}
The main idea here is to adapt the PCD framework so that Ursula
can combine the correctness proofs she computes for Bobs' requests in a single proof 
attesting to the following fact: ``Ursula has served $\omega$ distinct re-encryption 
requests correctly."

@@

\subsubsection{CoSi-based Scheme}
This solution utilizes the idea of collective signing by electing a committee 
that will sign a report submitted by a specific Ursula after verifying that 
the report supports the claim that ``Ursula has served $\omega$ distinct 
re-encryption requests correctly."

@@

\paragraph{On the committee election.} This can be done
by using some deterministic computation over a block hash and mapping
the output to Ursulas' public keys. So the selection is not determined by the
working Ursula to prevent any potential collusion. The selection may also take into account the presence and size of each Ursula's stake, to avoid an attacker spinning up enormous numbers of Ursulas in order to increase the chance of them controlling the entire committee.

@@

\paragraph{On the publicity of the signed records.} Having a 
valid collective signature from a committee (that has at least one honest 
member) suffices for the correctness of the signed statement. However, 
it could be better to keep the records that produced the message $m$  
available for a while so that any party can verify them (the verifying
parties could maintain such a public record for a given period after which
the logs can be discarded).

@@

\paragraph{On compensating the committee.} This solution may 
raise the question of why would the elected committee (especially if it 
is composed of other Ursulas in the system) participate in the CoSi 
process, which also involves verifying the full request record presented 
by the working Ursula. This can be pictured as a collaborative
work, the committee does the work so that others will do the same
when the committee members play the role of working Ursulas.

@@

\subsubsection{Challenge/Open-based Scheme}
This solution utilizes the idea of commit/challenge/open protocols. 
In details, Ursula keeps track of the requests coming from Bob(s) 
during a time round and assign each of them a unique sequence 
number. That is, Ursula replies with $cFrag$ and the correctness proof 
along with a sequence number showing the order of the request within 
the batch of requests handled during a round. At the end of the round, 
Ursula constructs a Merkle tree of all requests, where 
the requests (and their replies) are the leaves of the tree ordered by the sequence
numbers. Ursula signs the root of the tree, denoted as $root$ to produce 
a signature $\sigma_{root}$, then it publishes $(\omega, root, \sigma_{root})$ 
to the network (recall that $\omega$ is the number of served requests).

### 2020-03-23 tex/confirm-service-activity/threat-network-model.tex
reorganize the document

\section{Threat and Network Models}
\label{threat-network-model}
This section describes a modification for the network model of NuCypher 
required by the proposed confirm service activity solutions, in 
addition to the threat model we adopt in this document.

\subsection{Network Model}
In order for the proposed solutions to work, we need to ensure freshness, 
integrity, and authenticity of the requests issued by Bob. This can be achieved 
by requiring Bob to sign each request it issues and to include a timestamp, or 
sequence number, in each request to ensure freshness.

@@

\subsection{Threat Model}
We do not place trust in any party and we assume that all participants are 
self-interested. This means that a party may 
follow the protocol or deviate from it, either on its own or by colluding 
with other attackers, and decisions are solely based on what maximizes the financial profits
of this party. As such, Ursula may collude with Bob or Alice (by spinning 
its own Alice and/or Bob for example) to achieve her financial goals.

>>>>

\subsection{Threat and Network Models}
\label{threat-network-model}
This section describes a modification for the network model of NuCypher 
required by the proposed confirm service activity solutions, in 
addition to the threat model we adopt in this document.

\subsubsection{Network Model}
In order for the proposed solutions to work, we need to ensure freshness, 
integrity, and authenticity of the requests issued by Bob. This can be achieved 
by requiring Bob to sign each request it issues and to include a timestamp, or 
sequence number, in each request to ensure freshness.

@@

\subsubsection{Threat Model}
We do not place trust in any party and we assume that all participants are 
self-interested. This means that a party may 
follow the protocol or deviate from it, either on its own or by colluding 
with other attackers, and decisions are solely based on what maximizes the financial profits
of this party. As such, Ursula may collude with Bob or Alice (by spinning 
its own Alice and/or Bob for example) to achieve her financial goals.
